{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-05 Paper/main.tex
Small corrections

	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}}{i!}
	\end{equation}

	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can oftenlead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole. From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$. As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter. This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.

>>>>

	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

	But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion can often lead to reasonable approximations around a specific point or even on $\mathbb{R}$ as a whole. From this idea, it is natural to use the monomials as a potential basis to approximate functions in $\mathbb{L}^2[0,1]$. As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter. This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
